Automated Topic Naming

### 2012-01-19 ese/ese.tex
Alright I think we got that covered..
Almost done

\section{Understanding Software Maintenance Activities} 
\label{sec:analysis}
As we mentioned in the introduction, a key issue in software maintenance is understanding \emph{why} a system has evolved the way it has~\cite{aranda09icse}. 
In this section we demonstrate the value of labelled topic extraction
in addressing this issue. 
% more why
Labelled topics address \emph{why} questions by associating a commit with the underlying software qualities which motivated that change.
The \emph{how} of a change is the change itself, the software quality behind it, the
\emph{why} is what we are after.
We investigate the history of the three large-scale database systems that we studied. 
We use our technique to show the topic of development efforts over time in each project.
%We evaluated two research questions using the ground truth data that we annotated by hand:
We motivated our investigation with three research questions:
\renewcommand{\labelenumi}{\textbf{RQ\arabic{enumi}. }}
\begin{enumerate}
\item \emph{Do NFR frequencies change over time?} If a particular NFR
  was of more interest at one point in the life-cycle than another,
  this suggests that development activity shifted focus. For example,
  if a developer expected to see a recent focus on \emph{reliability},
  but instead \emph{usability} dominated, they might re-prioritize
  upcoming work items.

@@

We wanted to see whether developers in the PostgreSQL project\footnote{Since the MySQL and MaxDB data had poor records for developer ids, we focused on PostgreSQL.} worked on similar NFRs. For example, one developer might be a usability expert, while
another developer is focused on security. We assume that the NFR labels associated with a commit implicitly reflect work on those NFRs. Being able to report on where effort is being expended is useful for tracking productivity (among other things).
%Within this section we focused on PostgreSQL.
We explored this issue by extracting, for each topic in the PostgreSQL dataset, the developer names responsible for the commits used to generate that topic, and 
the NFRs that are associated with the topic. This produced a map which associated developer name with NFR labels. The six NFR labels (\emph{maintainability, usability, efficiency, functionality, portability, reliability}) and the \emph{None} label describe a 7-dimensional space, into which we can position developers, based on the frequency with which each label occurs in the map.

@@

\paragraph{External validity} -- %was addressed by our use of two case studies, but there are still issues. 
Our data originated from OSS database projects and thus might not be applicable to commercially developed software or other domains. 
Furthermore, our analysis techniques rely on a project's use of meaningful commit messages, although we feel this is the most frequently occurring form
of developer comments. 
While we tried to control for application domain variability, OSS
projects investigated were database systems, thus our results might
not generalize well to other domains.

>>>>

\section{Understanding Software Maintenance Activities} 
\label{sec:analysis}
%XXX Neil should we remove this cite?
As we mentioned in the introduction, a key issue in software
maintenance is understanding \emph{why} a system has evolved the way
it has: Aranda et al.~\cite{aranda09icse} explored \emph{why}, in
terms of how a bug actually occurred and was documented.
In this section we demonstrate the value of labelled topic extraction
in addressing this issue. 
% more why
Labelled topics address \emph{why} questions by associating a commit with the underlying software qualities which motivated that change.
The \emph{how} of a change is the change itself, the software quality behind it, the
\emph{why} is what we are after.
We investigate the history of the three large-scale database systems that we studied. 
We use our technique to show the topic of development efforts over time in each project.
%We evaluated two research questions using the ground truth data that we annotated by hand:
We motivated our investigation with three research questions:
\renewcommand{\labelenumi}{\textbf{RQ\arabic{enumi}. }}
\begin{enumerate}
\item \emph{Do NFR frequencies change over time?} If a particular NFR
  was of more interest at one point in the life-cycle than another,
  this suggests that development activity shifted focus. For example,
  if a developer expected to see a recent focus on \emph{reliability},
  but instead \emph{usability} dominated, they might re-prioritize
  upcoming work items.

@@

We wanted to see whether developers in the PostgreSQL project\footnote{Since the MySQL and MaxDB data had poor records for developer ids, we focused on PostgreSQL.} worked on similar NFRs. For example, one developer might be a usability expert, while
another developer is focused on security. We assume that the NFR labels associated with a commit implicitly reflect work on those NFRs. Being able to report on where effort is being expended is useful for tracking productivity (among other things).
%Within this section we focused on PostgreSQL.
We explored this issue by extracting, for each topic in the PostgreSQL dataset, the developer names responsible for the commits used to generate that topic, and 
the NFRs that are associated with the topic. 
The analysis in this section used Neil's annotations.
This produced a map which associated developer name with NFR labels. The six NFR labels (\emph{maintainability, usability, efficiency, functionality, portability, reliability}) and the \emph{None} label describe a 7-dimensional space, into which we can position developers, based on the frequency with which each label occurs in the map.

@@

\paragraph{External validity} -- %was addressed by our use of two case studies, but there are still issues. 
Our data originated from OSS database projects and thus might not be applicable to commercially developed software or other domains. 
Furthermore, our analysis techniques rely on a project's use of meaningful commit messages, although we feel this is the most frequently occurring form
of developer comments. 
While we tried to control for application domain variability, OSS
projects investigated were database systems, thus our results might
not generalize well to other domains. Generaizability is enhanced by
the fact that all three projects
were maintained by different developers and different teams using
different development processes.
